Predicting the 2024 US Presidential Election: A Polling-Based Forecast

### 2024-11-04 paper/paper.qmd
Modify the survey url and contact email
Signed-off-by: FrankFU323 <tianrui.fu@mail.utoronto.ca>

Survey Link: https://forms.gle/EzyHp3zuX8Cu6Ep8A

@@

Email: tianrui.fu@mail.utoronto.ca

@@

Email: yiyue.deng@mail.utoronto.ca

@@

Email: lijianing.li@mail.utoronto.ca

>>>>

Survey Link: [https://forms.gle/EzyHp3zuX8Cu6Ep8A](https://forms.gle/EzyHp3zuX8Cu6Ep8A)

@@

Email: [tianrui.fu@mail.utoronto.ca](tianrui.fu@mail.utoronto.ca)

@@

Email: [yiyue.deng@mail.utoronto.ca](yiyue.deng@mail.utoronto.ca)

@@

Email: [lijianing.li@mail.utoronto.ca](lijianing.li@mail.utoronto.ca)
